Generating Hubbard Model Solutions from Anderson Impurity Model Solutions

### 2021-08-05 notes.tex
added Anderson molecule diagonal Green's functions
wrote all four Greens functions for Anderson molecule, in expanded as well as compact notations

% !TEX TS-program = xelatex
\documentclass[12pt]{article}
\usepackage{amsthm,amsmath,amssymb,braket,graphicx,enumitem,booktabs,multirow,booktabs,tcolorbox,wrapfig,cancel,caption,fancyhdr,relsize,textpos,booktabs,tocbibind,titlesec}
\usepackage[margin=0.5in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[hidelinks,pdfusetitle]{hyperref}
\usepackage[stable]{footmisc}
\renewcommand{\arraystretch}{1.9}
\setlength\delimitershortfall{-2pt}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\fancyhead[L]{\nouppercase\leftmark}    
\fancyhead[R]{\thepage}    
\setlength{\headheight}{52pt}
\setcounter{tocdepth}{1}
\DeclareMathOperator{\sech}{sech}
\raggedbottom
\numberwithin{equation}{section}
\allowdisplaybreaks

@@

\section*{Appendix}
\subsection*{Spectra of Hubbard dimer and Anderson molecule}

@@

	\(-a_1\left(\pm U^A, t^A\right)\ket{\sigma,2} \pm a_2\left(\pm U^A, t^A\right)\ket{2, \sigma}\) & \(\ket{2\sigma_\pm}\) & \(\pm\frac{1}{4}\Delta(U^A, t^A)\)\\

@@

\subsection*{Local Greens function for the Hubbard dimer}

@@

\subsection*{Greens functions for Anderson molecule}
\begin{equation}\begin{aligned}
	G_{dd}^\uparrow(\omega) &= \sum_{n}\left[\frac{||\bra{n}c^\dagger_{d\uparrow}\ket{GS}||^2}{\omega + E_{GS} - E_n} + \frac{||\bra{n}c_{d\uparrow}\ket{GS}||^2}{\omega + E_n - E_{GS}}\right]\\
	G_{zz}^\uparrow(\omega)&= \sum_{n}\left[\frac{||\bra{n}c^\dagger_{z\uparrow}\ket{GS}||^2}{\omega + E_{GS} - E_n} + \frac{||\bra{n}c_{z\uparrow}\ket{GS}||^2}{\omega + E_n - E_{GS}}\right]\\
	G_{dz}^\uparrow(\omega)	&= \sum_{n}\left[\frac{\left<GS|c_{d\uparrow} | n \right>\left<n |c^\dagger_{z \uparrow} |GS\right>}{\omega + E_{GS} - E_n} + \frac{\left<n|c_{d\uparrow} | GS\right>\left<GS |c^\dagger_{z \uparrow} |n\right>}{\omega + E_{GS} - E_n}\right]\\
	G_{zd}^\uparrow(\omega) &= \sum_{n}\left[\frac{\left<GS|c_{z \uparrow} | n \right>\left<n |c^\dagger_{d \uparrow} |GS\right>}{\omega + E_{GS} - E_n} + \frac{\left<n|c_{z \uparrow} | GS\right>\left<GS |c^\dagger_{d \uparrow} | n\right>}{\omega + E_{n} - E_{GS}}\right]\\
\end{aligned}\end{equation}

>>>>

% !TEX TS-program = xelatex
\documentclass[12pt]{article}
\usepackage{amsthm,amsmath,amssymb,braket,graphicx,enumitem,booktabs,multirow,booktabs,tcolorbox,wrapfig,cancel,caption,fancyhdr,relsize,textpos,booktabs,tocbibind,titlesec}
\usepackage[margin=0.5in,bottom=0.6in]{geometry}
\usepackage[T1]{fontenc}
\usepackage[hidelinks,pdfusetitle]{hyperref}
\usepackage[stable]{footmisc}
\renewcommand{\arraystretch}{1.9}
\setlength\delimitershortfall{-2pt}
%\pagestyle{fancy}
%\fancyhf{}
%\fancyfoot{}
%\fancyhead[L]{\nouppercase\leftmark}    
%\fancyhead[R]{\thepage}    
%\setlength{\headheight}{52pt}
\setcounter{tocdepth}{1}
\DeclareMathOperator{\sech}{sech}
\raggedbottom
\numberwithin{equation}{section}
\allowdisplaybreaks

@@

\section*{Appendix: Spectra of Hubbard dimer and Anderson molecule}

@@

	\(a_1\left(U^A, t^A\right)\ket{\sigma,2} - a_2\left(U^A, t^A\right)\ket{2, \sigma}\) & \(\ket{2\sigma_-}\) & \(-\frac{1}{4}\Delta(U^A, t^A)\)\\
	\(a_2\left(U^A, t^A\right)\ket{\sigma,2} + a_1\left(U^A, t^A\right)\ket{2, \sigma}\) & \(\ket{2\sigma_+}\) & \(\frac{1}{4}\Delta(U^A, t^A)\)\\

@@

\section*{Appendix: Local Greens function for the Hubbard dimer}

@@

\section*{Appendix: Greens functions for Anderson molecule}
\begin{equation}\begin{aligned}
	G_{dd}^\uparrow(\omega) &= \sum_{n}\left[\frac{||\bra{n}c^\dagger_{d\uparrow}\ket{GS}||^2}{\omega + E_{GS} - E_n} + \frac{||\bra{n}c_{d\uparrow}\ket{GS}||^2}{\omega + E_n - E_{GS}}\right]\\
	G_{zz}^\uparrow(\omega)&= \sum_{n}\left[\frac{||\bra{n}c^\dagger_{z\uparrow}\ket{GS}||^2}{\omega + E_{GS} - E_n} + \frac{||\bra{n}c_{z\uparrow}\ket{GS}||^2}{\omega + E_n - E_{GS}}\right]\\
	G_{dz}^\uparrow(\omega)	&= \sum_{n}\left[\frac{\left<GS|c_{d\uparrow} | n \right>\left<n |c^\dagger_{z \uparrow} |GS\right>}{\omega + E_{GS} - E_n} + \frac{\left<n|c_{d\uparrow} | GS\right>\left<GS |c^\dagger_{z \uparrow} |n\right>}{\omega + E_{n} - E_{GS}}\right]\\
	G_{zd}^\uparrow(\omega) &= \sum_{n}\left[\frac{\left<GS|c_{z \uparrow} | n \right>\left<n |c^\dagger_{d \uparrow} |GS\right>}{\omega + E_{GS} - E_n} + \frac{\left<n|c_{z \uparrow} | GS\right>\left<GS |c^\dagger_{d \uparrow} | n\right>}{\omega + E_{n} - E_{GS}}\right] = \left\{G_{dz}^\uparrow(\omega)\right\}^\dagger\\
\end{aligned}\end{equation}
We proceed exactly as before. With the following shorthand notations,
\begin{equation}\begin{aligned}
	a_{1,2} &\equiv a_{1,2}\left(U^A, t^A\right), &&\tilde a_{1,2} \equiv a_{1,2}\left(\frac{1}{2}U^A, t^A\right) \\
	\Delta &\equiv \Delta\left(U^A, t^A\right), &&\tilde \Delta \equiv \Delta\left(\frac{1}{2}U^A, t^A\right)\\
	C_z^\pm &\equiv a_1 \tilde a_1 \pm a_2 \tilde a_2, &&C_x^\pm \equiv a_1 \tilde a_2 \pm a_2 \tilde a_1
\end{aligned}\end{equation}
\begin{equation}\begin{aligned}
	E_{\pm} \equiv E(\ket{2\sigma_\pm}) - E(\ket{-}) = E(\ket{0\sigma_\pm}) - E(\ket{-}) = \frac{1}{2}\tilde\Delta \pm \frac{1}{4}\Delta\\
\end{aligned}\end{equation}
the diagonal Green's functions are
\begin{equation}\begin{aligned}
	G_{d d}^\uparrow(\omega) &= \left[a_1\tilde a_2 + a_2\tilde a_1\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta - \frac{1}{4}\Delta\right]^2 } +\left[a_1\tilde a_1 - a_2\tilde a_2\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta\right]^2 }\\
				 &= {C_x^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_z^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }
\end{aligned}\end{equation}
\begin{equation}\begin{aligned}
	G_{z z}^\uparrow(\omega) &= \left[a_1\tilde a_1 + a_2\tilde a_2\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta - \frac{1}{4}\Delta\right]^2 } +\left[a_1\tilde a_2 - a_2\tilde a_1\right]^2\frac{\omega}{\omega^2 - \left[\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta\right]^2 }\\
				 &= {C_z^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_x^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }
\end{aligned}\end{equation}
and the off-diagonal Greens functions are
\begin{equation}\begin{aligned}
	G_{dz}^\uparrow(\omega) &= \left(a_1 \tilde a_1 + a_2 \tilde a_2\right) \left(a_1 \tilde a_2 + a_2 \tilde a_1\right) \frac{\frac{1}{4}\Delta - \frac{1}{2}\tilde\Delta}{\omega^2 - \left(\frac{1}{4}\Delta - \frac{1}{2}\tilde\Delta\right)^2} - \left(a_1 \tilde a_1 - a_2 \tilde a_2\right) \left(a_1 \tilde a_2 - a_2 \tilde a_1\right) \frac{\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta}{\omega^2  - \left(\frac{1}{2}\tilde\Delta + \frac{1}{4}\Delta\right)^2}\\
				&= -C_z^+ C_x^+ \frac{E_{-}}{\omega^2 - E_{-}^2} - C_z^- C_x^- \frac{E_{+}}{\omega^2  - E_{+}^2}\\
G_{zd}^\uparrow(\omega) &= {G_{dz}^\uparrow(\omega)}^\dagger = G_{dz}^\uparrow(\omega)
\end{aligned}\end{equation}
To summarize, the four Green's real space Greens functions, in the compact notation, of the Anderson molecule are
\begin{equation}\begin{aligned}
	G_{dd}^\uparrow(\omega) &= {C_x^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_z^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }\\
	G_{zz}^\uparrow(\omega) &= {C_z^+}^2\frac{\omega}{\omega^2 - E_{-}^2 } +{C_x^-}^2\frac{\omega}{\omega^2 - E_{+}^2 }\\
	G_{dz}^\uparrow(\omega) &= G_{zd}^\uparrow(\omega) = -C_z^+ C_x^+ \frac{E_{-}}{\omega^2 - E_{-}^2} - C_z^- C_x^- \frac{E_{+}}{\omega^2  - E_{+}^2}
\end{aligned}\end{equation}
